---
title: "Milestone2"
author: "Team 4"
date: "2025-07-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

For each of your (at least four) visualizations:

1) Display the visualization directly in your write-up if it is a static visualization, or include evidence of functionality as described in "How to Submit a Shiny App" in previous individual homework assignments. 

```{r}

```

2) Explain how to interpret the visualization and how it is relevant to the main questions/purpose of your project. Include at least one specific example of a takeaway a viewer can make from the graph. Please clearly relate your choices to the high-level goals and questions you explained in Milestone 1. If a design choice was inspired by your literature review, be sure to reference the specific existing visualization.

3) Finally, now that you see the design on your real data, please evaluate at least one strength and one weakness of each design, especially emphasizing cases where one design addresses a problem present in another. For example, there may be trade-offs in how densely packed the marks on a visualization are, how many different variables can be encoded, how intuitive a visualization is to understand, or how a visualization enables or hinders answering certain sub-questions of interest. 


